---
title: "Kaggle Tracy Regression Competition"
output:
  html_document: default
  html_notebook: default
---

This is a chunk of starter code to allow you to begin developing your scripts for the Kaggle Tracy Regression competition. To find the competition, go to https://www.kaggle.com/c/tracy-regression and read the overview of the competition. You can download the files from there.

Kaggle usually expects that the training and test files are in an input directory, so that is how this is configured.

I am using github, so my directories are in a github tree. First, we establish the working directory.

```{r}
library(ggplot2)

setwd("~/GitHub/DataScienceCurriculum/DataScienceCurriculum/DiamondRegression")

# read the input files

train = read.csv ("input/train.csv")
test = read.csv ("input/test.csv")
sample_submission = read.csv("input/sample_submission.csv")

head(train)
head(test)
head(sample_submission)

```

For a sample submission, just do a simple linear regression on the log of price vs. carat

```{r}

lmod = lm(log1p(price) ~ carat, data=train)

# it is necessary to cover the predicted values back to non-log values 
# use the exp function

train.predict <- exp(predict(lmod)) - 1
test.predict = exp(predict(lmod, newdata=test)) -1
benchmark_submission = sample_submission
benchmark_submission$price = test.predict
write.csv(benchmark_submission,"benchmark_submission.csv",row.names = F)

```

We can compute the RMSE of the log value with this code

```{r}

RSS <- c(crossprod(lmod$residuals))

MSE <- RSS / length(lmod$residuals)

#Root MSE:

RMSE <- sqrt(MSE)
RMSE

```

